Logarithmic Space Verifiers on NP-complete

### 2019-11-14 doc/manuscript.tex
Updated the content proof

Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}. A monotonically increasing function $f$ is not a constant and for every two values $x < y$ in the domain of $f$, then we obtain that $f(x) \leq f(y)$.

\begin{theorem}
\label{closed}
If $T(n)$ is a monotonically increasing function such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some monotonically increasing function $T'(n)$ when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes at most $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way. The existence of such function $G(n) > 1$ is possible because the family of languages $\textit{1TAPE}[T'(n)]$ is a subset of $P$ and thus $G(n) < 2^{n}$ \cite{Pap03}. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$. We could complete the end of the instance of size at most $G(n) \times n$ with the symbols that were not read during the deterministic two-way logarithmic space reduction just in the same order that appear in the original instance of size $n$.

@@

In this way, we obtain that every language in $\textit{1TAPE}[T'(n)]$ has a mapping to a corresponding language in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$. However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a monotonically increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.

Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$. Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance because of $T'(\frac{n}{G(n)}) < T'(n)$. Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances. Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotonically increasing function.
\end{proof}

@@

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. We can use this result when $T(n)$ is a monotonically increasing function as well \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}

>>>>

Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}. A strictly monotonically increasing function $f$ complies for every two values $x < y$ in the domain of $f$, then we obtain that $f(x) < f(y)$.

\begin{theorem}
\label{closed}
If $T(n)$ is a strictly monotonically increasing function such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some strictly monotonically increasing function $T'(n)$ when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes at most $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way. The existence of such function $G(n) > 1$ is possible because the family of languages $\textit{1TAPE}[T'(n)]$ is a subset of $P$ and thus $G(n) < 2^{n}$ \cite{Pap03}. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$. We could complete the end of the instance of size at most $G(n) \times n$ with the symbols that were not read during the deterministic two-way logarithmic space reduction just in the same order that appear in the original instance of size $n$.

@@

In this way, we obtain that every language in $\textit{1TAPE}[T'(n)]$ has a mapping to a corresponding language in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$. However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a strictly monotonically increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.

Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$. Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance because of $T'(\frac{n}{G(n)}) < T'(n)$. Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances. Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a strictly monotonically increasing function.
\end{proof}

@@

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. We can use this result when $T(n)$ is a strictly monotonically increasing function as well \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}
